Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
running example (with abstraction refinement) for AA

>>>>

\paragraph{Illustrative Example}

Let us take the Helicopter example in Table \ref{table:State-space benchmarks} with discretized dynamics
$$A_d = \left[\begin{array}{ccc}2.6207&-1.1793&0.65705\\2&0&0\\0&0.5&0\end{array}\right], B_d = \left [\begin{array}{c}8\\0\\0\end{array}\right]$$
Using an initial state $\bigwedge -.9 \leq x_{0,i} \leq .9$, inputs $-10 \leq u \leq 10$, and a safety specification $\bigwedge -.92 \leq x_i \leq .92$, the {\sc synthesize} phase in Fig.~\ref{fig:CEGARIS} synthesises an initial candidate controller $K=[\begin{array}{ccc}0.24609375&-0.125&0.1484375\end{array}]$.
Although this candidate is stable, the {\sc verify} phase finds it to be unsafe and returns a list of iterations with an example initial state that fails the safety specification
$(k,x_0) \in \{ (2, [\begin{array}{ccc}0.9&-0.9&0.9\end{array}]), (3, [\begin{array}{ccc}0.9&-0.9&-0.9\end{array}])\}$.
This allows the {\sc abstract} phase to create a new safety specification that considers these iterations for these initial states to constrain the solution space.
This refinement allows {\sc synthesize} to find a controller $K=[\begin{array}{ccc}0.23828125&-0.17578125&0.109375\end{array}]$, which this time passes the verification phase, resulting in a safe system.
